|

### 2020-04-10 R/README.Rmd
Update README files

This directory contains R script files used throughout the project. Each file 
contains one custom function or one data.frame which has been
documented using an roxygen2 skeleton.

After installing `candidaev`, an index of all the included 
functions/data.frames can be viewed in R using:

@@

>>>>

This directory contains R script files used throughout the project. Each file 
should only contain 1 function or dataset. Many of these functions have been
taken from the _Bioconductor_ package 
**[DEP](https://doi.org/10.18129/B9.bioc.DEP)**^1^, and adapted for use on
basic matrices instead of `SummarizedExperiment` objects.

After installing `candidaev`, an index of all the included 
functions/datasets can be viewed in R using:

@@

### References

1. Zhang, X., Smits, A., van Tilburg, G., Ovaa, H., Huber, W., Vermeulen, 
   M. (2018). Proteome-wide identification of ubiquitin interactions using UbIA-MS. 
   _Nature Protocols_, **13**, 530-550. 
   [doi:10.1038/nprot.2017.147](https://doi.org/10.1038/nprot.2017.147)

### 2020-04-10 README.Rmd
Accepted
Update README files

> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Bleackley, M. R., 
Anderson, M. A. (2020) Protein markers for _Candida albicans_ EVs include 
claudin-like Sur7 family proteins. _Journal of Extracellular_ 
_Vesicles_, submitted.

It has been permanently archived at Zenodo with the DOI shown above. The raw 
MS data has been deposited in the ProteomeXchange Consortium database via 
the PRIDE partner repository with the data set identifiers PXD014367, 
PXD014388, and PXD014389. The analysis techniques and workflow used in this 
compendium were derived from the _Bioconductor_ package 
**[DEP](https://doi.org/10.18129/B9.bioc.DEP)**^1^.

@@

```
    .
    ├── /R                   # Script files for functions and included data
    ├── /data-raw            # Raw data used (but not modified) in analyses
    ├── /data                # Data tables installed with package
    ├── /inst/manuscript     # Final submitted manuscript, figures, and supplementary data
    ├── /man                 # Auto-generated documentation for functions and included data
    ├── /vignettes           # Detailed examples of how analyses were performed
    ├── .Rbuildignore        # List of files and directories to ignore during R package build
    ├── .gitattributes       # List of files for github/linguist to ignore
    ├── .gitignore           # List of files to ignore during git commit
    ├── DESCRIPTION          # Research compendium metadata
    ├── LICENSE.md           # MIT License for code
    ├── NAMESPACE            # Auto-generated file for function export
    ├── README.Rmd           # Rmarkdown file to produce README.md
    ├── README.md            # Description of research compendium
    └── candidaev.Rproj      # R project file for compendium

@@

A partial installation will only install functions and data, which can be
used to analyse other MaxQuant `.txt` files.

@@

# install partial compendium (functions, data)
devtools::install_github("csdaw/candidaev", 
                         INSTALL_opts = "--no-inst")

# install full compendium (functions, data, vignettes, manuscript) 
# and other packages required to build vignettes and manuscript
devtools::install_github("csdaw/candidaev", 
                         build_opts = c("--no-resave-data", "--no-manual"), 
                         dependencies = TRUE, build_vignettes = TRUE)
```

@@

The manuscript `.docx` file, as submitted, can be downloaded 
[here](https://github.com/csdaw/candidaev/tree/master/inst/manuscript).

>>>>

> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A., 
Bleackley, M. R. (2020) Protein markers for _Candida albicans_ EVs include 
claudin-like Sur7 family proteins. _Journal of Extracellular_ 
_Vesicles_, x(x): 1750810. DOI: 
[10.1080/20013078.2020.1750810](https://doi.org/10.1080/20013078.2020.1750810)

It has been permanently archived at Zenodo with the DOI shown below. The raw 
MS data has been deposited in the ProteomeXchange Consortium database via 
the PRIDE partner repository with the data set identifiers PXD014367, 
PXD014388, and PXD014389. The analysis techniques and workflow used in this 
compendium were derived from the _Bioconductor_ package 
**[DEP](https://doi.org/10.18129/B9.bioc.DEP)**^1^.

@@

```
    ./
    ├── R                    # Script files for functions and included datasets
    ├── data-raw             # Raw data used (but not modified) in analyses
    ├── data                 # Datasets included with package
    ├── inst/manuscript      # Final accepted manuscript, figures, and supplementary data
    ├── man                  # Auto-generated documentation for functions and included data
    ├── vignettes            # Detailed examples of how analyses were performed
    ├── .Rbuildignore        # List of files and directories to ignore during R package build
    ├── .gitattributes       # List of files for github/linguist to ignore
    ├── .gitignore           # List of files to ignore during git commit
    ├── DESCRIPTION          # Research compendium metadata
    ├── LICENSE.md           # MIT License for code
    ├── NAMESPACE            # Auto-generated file for function export
    ├── README.Rmd           # Rmarkdown file to produce README.md
    ├── README.md            # Description of research compendium
    └── candidaev.Rproj      # R project file for compendium

@@

A partial installation will only install functions, datasets, which can be
used to analyse other MaxQuant `.txt` files with _Candida albicans_ LFQ data.
The manuscript will also be installed, but the vignettes won't be available.

@@

# install partial compendium (functions, datasets, manuscript)
devtools::install_github("csdaw/candidaev", 
                         INSTALL_opts = "--no-inst")

# install full compendium (functions, datasets, manuscript, vignettes) 
# and other packages required to build vignettes and manuscript
devtools::install_github("csdaw/candidaev", 
                         build_opts = c("--no-resave-data", "--no-manual"), 
                         dependencies = TRUE, build_vignettes = TRUE)
```

@@

The manuscript `.docx` file, as accepted, can be downloaded 
[here](https://github.com/csdaw/candidaev/tree/master/inst/manuscript).

### 2020-04-10 data-raw/README.Rmd
Update README files

# /data-raw

## Description
This directory contains all of the raw data files used in this project. 
These files are *not* included when the package is installed using 
`devtools::install_github()`. Rather *'clean'* versions of the `.csv` and 
`.tab` files are provided in the [`/data`](../data) folder as `.rda` files 
which are accessible once the package has been installed and loaded or attached.

@@

## Contents
```
    .
    ├── ...
    ├── /data-raw
    │    ├── /lcms           # proteinGroups.txt files output by MaxQuant
    │    ├── /nta            # Nanosight NS300 .csv summary tables
    │    ├── /reference      # UniProt and Candida Genome Database reference tables
    │    ├── README.Rmd      # R markdown file to produce README.md
    │    └── README.md       # Description of /data-raw directory
    └── ...

>>>>

# data-raw

## Description

This directory contains all of the raw data files used in this project. 
These files are *not* included when the package is installed using 
`devtools::install_github()`. Rather *'clean'* versions of the `.csv` and 
`.tab` files are provided in the [`/data`](../data) folder as `.rda` files 
which are accessible once the package has been installed and loaded or attached.

@@

## Contents
```
    .
    ├── ...
    ├── data-raw
    │    ├── lcms            # proteinGroups.txt files output by MaxQuant
    │    ├── nta             # Nanosight NS300 .csv summary tables
    │    ├── reference       # UniProt and Candida Genome Database reference tables
    │    ├── README.Rmd      # R markdown file to produce README.md
    │    └── README.md       # Description of data-raw directory
    └── ...

### 2020-04-10 inst/manuscript/README.Rmd
Update README files

# /inst/manuscript

@@

This directory contains the submitted manuscript, supplemental figures and 
tables, and supplemental files for our paper:

> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A., 
Bleackley, M. R. (2019) Protein markers for _Candida albicans_ EVs include 
claudin-like Sur7 family proteins and Rho GTPases. Mol. Cell. Proteomics, 
submitted.

The Rmarkdown (`.Rmd`), `.svg`, and `.R` files used to generate these 
documents are provided along with the derived `.pdf` and `.csv` files.

## Contents
```
    .
    ├── ...
    ├── /inst
    │    ├── /manuscript
    │         ├── /components                 # Contains required components for building the manuscript
    │         ├── /figures                    # Contains .svg and .csv files used to make some figures
    │         ├── /supplement_files           # Contains .R scripts used to generate supplemental files
    │         ├── manuscript.Rmd              # R markdown file to produce manuscript.pdf
    │         ├── manuscript.pdf              # Final submitted manuscript
    │         ├── manuscript_supplement.Rmd   # R markdown file to produce manuscript_supplement.pdf
    │         ├── manuscript_supplement.pdf   # Final submitted supplemental figures and tables
    │         ├── README.Rmd                  # R markdown file to produce README.md
    │         └── README.md                   # Description of /inst/manuscript directory
    └── ...

>>>>

# inst/manuscript

@@

This directory contains the submitted manuscript and supplement `.docx` files, 
main figures, supplementary figures, supplementary data for our paper:

> Dawson, C. S., Garcia-Ceron, D., Rajapaksha, H., Faou, P., Anderson, M. A., 
Bleackley, M. R. (2020) Protein markers for _Candida albicans_ EVs include 
claudin-like Sur7 family proteins. _Journal of Extracellular_ 
_Vesicles_, x(x): 1750810. DOI: 
[10.1080/20013078.2020.1750810](https://doi.org/10.1080/20013078.2020.1750810)

The scripts used to generate the figures, tables, and supplementary data are
also present. This directory is automatically installed when the `candidaev`
package is installed.

## Contents
```
.
├── ...
├── inst
│    ├── manuscript
│         ├── components                        # Required components for building the manuscript
│         ├── figures                           # Individual high resolution files for each figure
|         ├── tables                            # Tables as .docx files
│         ├── supplementary_data                # Supplementary data and scripts to generate them
│         ├── README.Rmd                        # Rmarkdown file to produce README.md
│         ├── README.md                         # Description of inst/manuscript directory
│         ├── candidaev_manuscript_FINAL.docx   # Manuscript as accepted
│         ├── candidaev_supplement_FINAL.docx   # Supplement figure and table legends
│         ├── candidaev_figures.pdf             # Main figures and table as accepted
│         ├── candidaev_figures.Rmd             # Script to produce main figures and table
│         ├── candidaev_supplement.pdf          # Supplementary figures and tables as accepted
│         └── candidaev_supplement.Rmd          # Script to produce supplementary figures and tables
└── ...
